The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-22 paper.tex
update

\begin{table*}[t]
\raggedright
\caption{Parameters of the disc, atmosphere, and gravitational potential in the simulation.}
\label{table-parameters}
\begin{tabular}{@{}llrc@{}}
\toprule[1pt]\midrule[0.3pt]
Parameter                             & Description                               & Value                                &  Reference                     \\ \midrule
{\bf Static stellar potential }       &                                           &                                      &                                \\
$\sigma_{\text{bulge}}$               & Velocity dispersion of bulge              & 100 km$\cdot$s$^{-1}$                & \citep{velocity-dispersion-MW} \\
$\rho_{\text{bulge}}^{\text{peak}}$   & Peak average density of bulge             & $4\times 10^{-24}$ g$\cdot$cm$^{-3}$ &   N/A                          \\ \hline
{\bf Static dark halo potential }     &                                           &                                      &                                \\
$v_{\text{halo}}$                     & Characteristic velocity                   & 131.5 km$\cdot$s$^{-1}$              & \citep{Johnston1995}           \\
$d_{\text{h}}$                        & Core radius                               & 12 kpc                               & \multicolumn{1}{c}{''}         \\ \hline
{\bf Atmosphere }                     &                                           &                                      &                                \\
$T_{\text{\text{atmp}}}$              & Temperature of atmosphere                 & $10^{6}$ K                           & \citep{temperature-MW}         \\ \hline
{\bf Isothermal disc }                &                                           &                                      &                                \\
$z_{0}$                               & Scale height of disc                      & 100 pc                               & \citep{peak-ism-density}       \\
$T_{\text{\text{isoDisk}}}$           & Temperature of disc                       & $10^{3}$ K                           & \multicolumn{1}{c}{''}         \\
$\rho_{\text{isoDisk}}^{\text{peak}}$ & Peak mass density of disc                 & $10^{-23}$ g$\cdot$cm$^{-3}$         & \multicolumn{1}{c}{''}         \\ \hline
{\bf Clumpy disc }                    &                                           &                                      &                                \\
$\dagger$  $k_{\text{min}}$           & Cutoff wave number                        & 375.0                                & \citep{peak-ism-density}       \\
$\mu$                                 & Mean of scalar field                      & 1.0                                  &   N/A                          \\
$\ddag$  $\sigma$                     & Dispersion of scalar field                & 5.0                                  & \citep{Federrath2010}          \\
$\beta$                               & Power law index                           & -5/3                                 &   N/A                          \\ \midrule
\end{tabular}
\begin{tablenotes}
      \raggedright
      \item  $\dagger$  $k_{\text{min}}=375.0$ leads to the size of an individual molecular cloud $\sim 100$ pc.
      \item  $\ddag$ In numerical simulations of turbulence,\
             \citet{Federrath2010} find $\sigma\sim 3.6$ and 35 for solenoidal (divergence-free)\
             and compressive (curl-free) driving force,\
             respectively, so that our adopted value of 5 is closer to their solenoidal result.
    \end{tablenotes}
\end{table*}

@@

  First, we observe that\
  The simulated eROSITA bubbles are not as limb-brightened as the observation.\
  A possibility to enhance the X-ray emission is to include shock-accelerated CRs near the shock,\
  in which CRs could increase the compressibility of the fluid,\
  resulting in the enhanced thermal Bremsstrahlung emissivity that is proportional to density.
  The broad agreement between simulated and observed X-ray maps hints that\
  the full vertical extent of the eROSITA bubbles can be properly formed by an oblique jet within a thin disk\
  of dense ISM.

@@

\item The Galactic bubbles are nearly symmetric about the Galactic plane albeit\
      the bipolar jets are at an angle $45^{\circ}$\
      with respect to the disc normal.\
      The broad agreement between simulated and observed multiwavelength features\
      provides supporting evidence for the oblique jet scenario, and also\
      releases the caveat given by earlier simulation-based studies:\
      the jets shall be vertical to the disc normal.
\item The randomness of clumpy disk has a insignificant impact on the overall dynamic of the Galactic bubbles.\
      The development of the reverse shocks (the innermost bubbles) are always associated with the dense disc,\
      without the disc, the outermost bubbles and the turbulent plasma will be oblique,\
      indicating the dense disc is crucial for\
      the symmetry of the Galactic bubbles and for the innermost bubbles formation.
\item The edge of the eROSITA bubbles is a forward shock,\
      originally driven by oblique bipolar jets emanating from the GC 12.39 million years ago,\
      and significantly stretched by the stratified atmosphere afterwards.\
      The simulated eROSITA bubbles are not as limb-brightened as the observation.\
      A possibility to enhance the X-ray emission is to include shock-accelerated CRs near the shock,\
      in which CRs could increase the compressibility of the fluid,\
      resulting in the enhanced thermal Bremsstrahlung emissivity that is proportional to density.
\item Followed by the forward shock is a tangling contact discontinuity,\
      which we interpret as the edge of the \textit{Fermi} bubbles.\
      The nature of the \textit{Fermi} bubbles is essentially a turbulent and high-temperature ($\sim2$ keV)\
      plasma in pressure balance with the external medium. Associated with the Galactic magnetic field\
      will lead to the stochastic acceleration of CRe, and probably balanced with the IC and synchrotron cooling.\
      We will investigate the competition between stochastic acceleration and radiative cooling in a future work.
\item According to the microwave and leptonic gamma-ray spectra, the best-fitting\
      CRe power-law index is found to be 2.4.
\item The same leptotonic CRe can simultaneously\
      account for the \textit{Fermi} bubbles and haze emission suggested that\
      they are physically related around the GC,\
      and that the magnetic fields within the bubbles are close to the exponentially distributed\
      Galactic magnetic field.
\end{itemize}

>>>>

\begin{table*}[t]
\raggedright
\caption{Parameters of the disc, atmosphere, and gravitational potential in the simulations.}
\label{table-parameters}
\begin{tabular}{@{}llrc@{}}
\toprule[1pt]\midrule[0.3pt]
Parameter                             & Description                               & Value                                &  Reference                     \\ \midrule
{\bf Static stellar potential }       &                                           &                                      &                                \\
$\sigma_{\text{bulge}}$               & Velocity dispersion of bulge              & 100 km$\cdot$s$^{-1}$                & \citep{velocity-dispersion-MW} \\
$\rho_{\text{bulge}}^{\text{peak}}$   & Peak average density of bulge             & $4\times 10^{-24}$ g$\cdot$cm$^{-3}$ &   N/A                          \\ \hline
{\bf Static dark halo potential }     &                                           &                                      &                                \\
$v_{\text{halo}}$                     & Characteristic velocity                   & 131.5 km$\cdot$s$^{-1}$              & \citep{Johnston1995}           \\
$d_{\text{h}}$                        & Core radius                               & 12 kpc                               & \multicolumn{1}{c}{''}         \\ \hline
{\bf Atmosphere }                     &                                           &                                      &                                \\
$T_{\text{\text{atmp}}}$              & Temperature of atmosphere                 & $10^{6}$ K                           & \citep{temperature-MW}         \\ \hline
{\bf Isothermal disc }                &                                           &                                      &                                \\
$z_{0}$                               & Scale height of disc                      & 100 pc                               & \citep{peak-ism-density}       \\
$T_{\text{\text{isoDisk}}}$           & Temperature of disc                       & $10^{3}$ K                           & \multicolumn{1}{c}{''}         \\
$\rho_{\text{isoDisk}}^{\text{peak}}$ & Peak mass density of disc                 & $10^{-23}$ g$\cdot$cm$^{-3}$         & \multicolumn{1}{c}{''}         \\ \hline
{\bf Clumpy disc }                    &                                           &                                      &                                \\
$\dagger$  $k_{\text{min}}$           & Cutoff wave number                        & 375.0                                & \citep{peak-ism-density}       \\
$\mu$                                 & Mean of scalar field                      & 1.0                                  &   N/A                          \\
$\ddag$  $\sigma$                     & Dispersion of scalar field                & 5.0                                  & \citep{Federrath2010}          \\
$\beta$                               & Power law index                           & -5/3                                 &   N/A                          \\ \midrule
\end{tabular}
\begin{tablenotes}
      \raggedright
      \item  $\dagger$  $k_{\text{min}}=375.0$ leads to the size of an individual molecular cloud $\sim 100$ pc.
      \item  $\ddag$ In numerical simulations of turbulence,\
             \citet{Federrath2010} find $\sigma\sim 3.6$ and 35 for solenoidal (divergence-free)\
             and compressive (curl-free) driving force,\
             respectively, so that our adopted value of 5 is closer to their solenoidal result.
    \end{tablenotes}
\end{table*}

@@

  First, we observe that\
  The simulated eROSITA bubbles are not as limb-brightened as the observation.\
  A possibility to enhance the X-ray emission is to include shock-accelerated CRs near the shock,\
  in which CRs could increase the compressibility of the fluid,\
  resulting in the enhanced thermal Bremsstrahlung emissivity that is proportional to density squared.
  The broad agreement between simulated and observed X-ray maps hints that\
  the full vertical extent of the eROSITA bubbles can be properly formed by an oblique jet within a thin disk\
  of dense ISM.

@@

\item The Galactic bubbles are nearly symmetric about the Galactic plane albeit\
      the bipolar jets are at an angle $45^{\circ}$\
      with respect to the disc normal.\
      The broad agreement between simulated and observed multiwavelength features\
      provides supporting evidence for the oblique jet scenario, and also\
      releases the caveat given by earlier simulation-based studies:\
      the jets shall be vertical to the disc normal.
\item The randomness of clumpy disk has a insignificant impact on the overall dynamic of the Galactic bubbles.\
      The development of the reverse shocks (the innermost bubbles) are always associated with the dense disc,\
      without the disc, the outermost bubbles and the turbulent plasma will be oblique,\
      indicating the dense disc is crucial for\
      the symmetry of the Galactic bubbles and for the innermost bubbles formation.
\item The edge of the eROSITA bubbles is a forward shock,\
      originally driven by oblique bipolar jets emanating from the GC 12.39 million years ago,\
      and significantly stretched by the stratified atmosphere afterwards.\
      The simulated eROSITA bubbles are not as limb-brightened as the observation.\
      A possibility to enhance the X-ray emission is to include shock-accelerated CRs near the shock,\
      in which CRs could increase the compressibility of the fluid,\
      resulting in the enhanced thermal Bremsstrahlung emissivity that is proportional to density squared.
\item Followed by the forward shock is a tangling contact discontinuity,\
      which we interpret as the edge of the \textit{Fermi} bubbles.\
      The nature of the \textit{Fermi} bubbles is essentially a turbulent and high-temperature ($\sim2$ keV)\
      plasma in pressure balance with the external medium. Associated with the Galactic magnetic field\
      will lead to the stochastic acceleration of CRe, and probably balanced with the IC and synchrotron cooling.\
      We will investigate the competition between stochastic acceleration and radiative cooling in a future work.
\item According to the microwave and leptonic gamma-ray spectra, the best-fitting\
      CRe power-law index is found to be 2.4.
\item The same leptotonic CRe can simultaneously\
      account for the \textit{Fermi} bubbles and haze emission suggested that\
      they are physically related around the GC,\
      and that the magnetic fields within the bubbles are close to the exponentially distributed\
      Galactic magnetic field.
\end{itemize}
